Equations & R Code

### 2017-03-08 manuscript/coexistence-stability_SI.Rmd
updates SI text with two Rmu over large sigE gradient figure

Condition 1 is already included in our main analysis (Figures 2 and 4).
Condition 2 simply creates conditions where some species cannot coexist, which would not change the relationship between species richness and ecosystem variability, but rather disallow it.
Condition 3 is more interesting, because it could create situations where species may not coexist, but it could also weakn the diversity--ecosystem variabilty relationship be reducing mean biomass and the effect of species with very nonlinear growth rates.
To explore the effect of condition 3, we ran simulations across a gradient of resource variability (11 levels) crossed with a gradient of mean resource levels (3 levels).

@@

>>>>

Condition 1 is already included in our main analysis (Figures 2 and 4).
Condition 2 simply creates conditions where some species cannot coexist, which would not change the relationship between species richness and ecosystem variability, but rather disallow it.
Condition 3 is more interesting, because it could create situations where species may not coexist, but it could also weaken the diversity--ecosystem variabilty relationship be reducing mean biomass and the effect of species with very nonlinear growth rates.
To explore the effect of condition 3, we ran simulations across a gradient of resource variability (11 levels) crossed with a gradient of mean resource levels (3 levels).

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=5in]{./components/SI_storage_effect_two_rmus_fourSpeciesOnly.png}
  \caption{Ecosystem \emph{CV} of a four-species community as a function of environmental cue variance at two levels of mean resource availability (\texttt{Rmu} across tops of panels) and two levels of correlation of species' responses to environmental conditions ($\rho$). Here we simualted community dynamics across a greater range of environmental cue variance (up to 10) to show that the \emph{CV} of four-species communities does not remain flat as environmental variance increases beyond levels shown in the main text. The mean resource level has no effect on the results.}
\end{figure}
